Exploring dimensions of biodiversity in Japanese ferns

### 2020-06-30 ms/manuscript.Rmd
Use species_motifs_ferns_8L instead of species_motifs_ferns

loadd(list = c(
  "occ_point_data_ferns",
  "ses_phy_ferns",
  "ses_phy_ferns_endemic",
  "ses_traits_ferns",
  "shape_ferns",
  "k_taxonomy",
  "k_phylogeny",
  "regions_taxonomy",
  "regions_phylogeny",
  "species_motifs_ferns"
),
cache = ja_fern_cache)

@@

omega <-
species_motifs_ferns$omega %>%
  as.data.frame %>%
  rownames_to_column("site") %>%
  left_join(centroids, by = "site") %>%
  column_to_rownames("site")

>>>>

loadd(list = c(
  "occ_point_data_ferns",
  "ses_phy_ferns",
  "ses_phy_ferns_endemic",
  "ses_traits_ferns",
  "shape_ferns",
  "k_taxonomy",
  "k_phylogeny",
  "regions_taxonomy",
  "regions_phylogeny",
  "species_motifs_ferns_8L"
),
cache = ja_fern_cache)

@@

omega <-
species_motifs_ferns_8L$omega %>%
  as.data.frame %>%
  rownames_to_column("site") %>%
  left_join(centroids, by = "site") %>%
  column_to_rownames("site")
